Gender and international diversity improves equity in peer review

### 2019-01-19 analysis_v1/eLife_Analysis_and_Figures.Rmd
mvoed old scripts and notebook into new folder

## Setup
The first step is to set up the environment. We import all the required pacakges and setup our custom ggplot theme. We also define here a simple function that is used to convert p-balues to a series of astericks, and another function that capitalizes the first letter of a word, used for capitalizing place names. 
```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(readr)
library(readxl)
library(gridExtra)
library(grid)
library(tidyr)

@@

```{r message=FALSE}
# Load the main eLife data file
elife <- read_excel("~/Dropbox/eLife/data/elife_datafile.xlsx")

# exclude the article type "Scientific Correspondance"
elife <- elife %>% filter(type.x != "RE")

# Load the country infomration .csv file, which was manually created and available along with this file
country_mapping <- read_csv("~/Dropbox/eLife/data/elife_countries.csv")

@@

@@

    # Flag data if full submission has been submitted, but no decision has been made (ie: still in revision or decision stage)
    full_decision_made = !is.na(full_submission_date) & last(na.omit(c(full_decision, rev1_decision, rev2_decision))) != "Revise",

@@

    # Now add variables relating to the composition of the reviewer team
    # Quality of list variables—list of the names, countries, and genders of reviewers
    reviewer_names = list(tolower(na.omit(c(bre_name, reviewer1_name, reviewer2_name, reviewer3_name, reviewer4_name)))),
    reviewer_genders = list(na.omit(c(bre_gender, reviewer1_gender, reviewer2_gender, reviewer3_gender, reviewer4_gender))),
    reviewer_countries = list(tolower(na.omit(c(bre_country, reviewer1_country, reviewer2_country, reviewer3_country, reviewer4_country)))),
    reviewer_continents = list(tolower(na.omit(c(bre_continent, reviewer1_continent, reviewer2_continent, reviewer3_continent, reviewer4_continent)))),

@@

@@

@@

@@

@@

elife <-elife %>%
  # Now lets remove any identifying information, ie: names and institutions. We also remove country/continent for gatekeepers, as the population is smaller
  # We also remove all dates and times, because thees could probably be used to identify information about a particular manuscript
  # Also, lets remove variables that we will not prefently be working with, just to keep the table clean
  select(-c(ca_name, la_name, fa_name,  se_name, bre_name, reviewer1_name, reviewer2_name, reviewer3_name, reviewer4_name, 
         ca_institution, la_institution, fa_institution, se_institution, bre_institution, 
         reviewer1_institution, reviewer2_institution, reviewer3_institution, reviewer4_institution,
         se_country, bre_country, se_continent, reviewer1_country, reviewer2_country, reviewer3_country, reviewer4_country,
         initial_submission_time, full_submission_date, rev1_submission_date, rev2_submission_date,
         initial_decision_time, full_decision_date, rev1_decision_date, rev2_decision_date, submission_month,
         deltatime_initial_submission_decision,	deltatime_full_submission_decision,	deltatime_initial_submission_to_accept,	deltatime_full_submission_to_accept,
         deltatime_rev1,	deltatime_rev2,	revision_time,	deltatime_final,
         prop_male_reviewers, prop_female_reviewers, appeal_state1, appeal_state2, appeal_state3, type.x, type.y, 
         reviewer_names, reviewer_countries, reviewer_continents, reviewer_genders, full_decisions,
         reviewer_names_nobre, reviewer_genders_nobre))

# write this file as output, so that future analysis can start from this file as a checkpoint
write.csv(elife, "formatted_data/formatted_elife.csv")

write.csv(people, "formatted_data/elife_people.csv")

@@

## Checkpoint
Here we load the data that was manipulated in the previous code chunk. Skip to here if the original (non-anonymized) data is not available.
```{r}
elife <- read.csv("formatted_data/formatted_elife.csv")
```

@@

fig4 <- data_fig4 %>%
  ggplot(aes(x = gender, y = measurement, color = factor(gender), shape = factor(gender), fill = factor(gender))) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, color = "black") +
  geom_text(aes(x = 1.5, y = 0.59, label = ifelse(measure_key == "Submissions", "", as.character(sig))), color = "black") +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.58, 1.1), yend = ifelse(sig != "N/A", 0.58, 1.1)), color = "black") +
  #facet_grid(author_key ~ measure_key) +
  facet_wrap(~author_key) +
  coord_cartesian(ylim = c(0.4, 0.6)) +
  theme_dakota() +
  guides(fill = F) +
  labs(
    x = "Gender of Author",
    y = "% of full submissions accepted"
  )

@@

data_fig5 <- elife %>%
  filter(initial_decision_made & full_decision_made & !is.na(composition)) %>%
  mutate(total_submissions = n()) %>%
  gather(author_key, value = gender, la_gender) %>%
  filter(gender %in% c("M", "F")) %>%
  group_by(composition, author_key, gender) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE),
    acceptance_rate = sum(accepted == TRUE) / paper_count,
    standard_error = 1.96 * sqrt( (acceptance_rate * (1 - acceptance_rate)) / paper_count),
    lower = acceptance_rate - standard_error,
    upper = acceptance_rate + standard_error
  ) %>%
  ungroup() %>%
  left_join(sig_df, by = c("composition", "author_key")) %>%
  mutate(
    author_key = factor(author_key,
                        levels = c("ca_gender", "fa_gender", "la_gender"),
                        labels = c("ca_gender" = "Corresponding", "fa_gender" = "First", "la_gender" = "Last"))
    ,
    gender = ifelse(gender == "M", "Male", "Female"),
    composition = factor(composition, labels = c("All Men" = "All-male reviewers", "All Women" = "All-female reviewers", "Mixed" = "Mixed-gender reviewers", "Uncertain" = "Uncertain"))
  ) %>%
  filter(composition != "Uncertain")

fig5 <- data_fig5 %>% 
  ggplot(aes(x = gender, y = acceptance_rate, fill = gender)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_text(aes(y = 0.31, label = paper_count), size = 3.5, color = "black") +
  #geom_text(aes(y = 0.1, label = paste0(round(acceptance_rate, 3) * 100, "%")), size = 2.5, color = "black", position = position_dodge(0.87)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, color = "black", alpha = 0.8) +
  geom_text(aes(x = 1.5, y = 0.76, label = sig), color = "black") +
  #geom_text(aes(x = gender, y = 0.1, label = round(acceptance_rate, 3) * 100 ), color = "black") +
  geom_segment(aes(x = 1.1, xend = 1.9, y = ifelse(sig != "N/A", 0.74, 1.1), yend = ifelse(sig != "N/A", 0.74, 1.1)), color = "black") +
  facet_wrap( ~composition) +
  coord_cartesian(ylim = c(0.30, 0.8)) +
  theme_dakota() +
  guides(fill = F) +
  labs(y = "% of full submissions accepted",
       x = "Gender of Last Author"
  )

@@

@@

### Proportion of intiial submissions constituted by top 8 counties
```{r}
sum(data_table$`Prop. of Initial Submissions`)
```

### Proportion of full submissions constituted by top 8 counties
```{r}
sum(data_table$`Prop. of Full Submissions`)
```

### Proportion of accepted submissions constituted by top 8 counties
```{r}
sum(data_table$`Prop. of Accepted Submissions`)
```

@@

```{r message=FALSE, warning=FALSE}
countries <- c("canada", "china", "france", "germany", "japan", "switzerland", "united kingdom", "united states")
sig_list <- list()
for (country in countries) {
  s <- subset(elife, full_decision_made == T & has_full_submission & ca_country == country)
  t <- table(s$ca_country_homophily, s$accepted)
  test = chisq.test(t[, 1:2])
  sig_list[length(sig_list) + 1] <- list(country = test)
}

@@

@@

fig7.B <- d1.summ %>%
  union(d2.summ) %>%
  union(d3.summ) %>%
  left_join(sig_df, by = "type") %>%
  mutate(type = factor(type, 
                       levels = c("all", "no us", "no founder"),
                       labels = c("All Countries", "Excluding U.S.", "Excluding Founding Nations")
                       )
         ) %>%
  ggplot(aes(x = ca_country_homophily, y = encourage_accept_rate, fill = ca_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 0.32), size = 2.5) +
  geom_text(aes(label = sig, x = 1.5, y = 0.65)) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.6, 1.1), yend = ifelse(sig != "N/A", 0.6, 1.1)), color = "black") +
  facet_wrap(~type, nrow = 3) +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  theme_dakota() +
  guides(fill = FALSE) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  labs(
    x = "",
    y = "% of full submissions accepted"
  )

fig7 <- grid.arrange(fig7.B, fig7.A, ncol = 2, widths = 1:2)

ggsave("figures/main/fig_7.tiff", plot = fig7, height = 5, width = 7.5)
ggsave("figures/main/fig_7.png", plot = fig7, height = 5, width = 7.5)
```

@@

p2 <- elife %>%
  filter(initial_decision_made & (full_decision_made | full_decision_date_isNA) & !is.na(ca_country)) %>%
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>% # capitalize first letter of country stirngs
  group_by(ca_country) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_count = sum(encouraged == TRUE, na.rm = T),
    encourage_rate = encourage_count / paper_count,
    accept_rate = accept_count / sum(!has_full_submission | full_decision_made, na.rm = T),
    encourage_accept_rate = accept_count / sum(has_full_submission & full_decision_made, na.rm = T)
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  top_n(16, totals) %>%
  mutate(
    ca_country = reorder(ca_country, encourage_accept_rate)
  ) %>%
  gather(measure_key, value = measurement, encourage_rate, accept_rate, encourage_accept_rate) %>%
  mutate(measure_key = factor(measure_key, 
                           levels = c("encourage_rate", "encourage_accept_rate", "accept_rate"),
                           labels = c("encourage_rate" = "% of initial submissions encouraged", 
                                      "encourage_accept_rate" = "% of full submissions accepted",
                                      "accept_rate" = "% of initial submissions accepted"
                                      )
                           ) # end factor
  ) %>%
  group_by(measure_key) %>%
  mutate(
    se = 1.96 * sqrt(measurement * (1 - measurement) / paper_count),
    lower = measurement - se,
    upper = measurement + se
  ) %>%
  ggplot(aes(x = ca_country, y = measurement)) +
  geom_bar(stat = "identity", color = "black", fill = "dodgerblue4", alpha = 0.8) +
  geom_text(aes(y = upper, label = paste0(round(measurement, 3) * 100, "%")), size = 2.5, hjust = -0.4, family = "Times") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  facet_wrap(~measure_key, labeller = labeller(key = labels)) +
  theme_dakota() +
  labs(y = "%") +
  coord_flip() +
  ylim(0, 0.75) +
  theme(
    axis.title.y = element_blank()
  )

>>>>

## Setup
The first step is to set up the environment. We import all the required pacakges and setup our custom ggplot theme. We also define here a simple function that is used to convert p-balues to a series of astericks, and another function that capitalizes the first letter of a word, used for capitalizing place names. 
```{r, message=FALSE, warning=FALSE}
library(readr)
library(readxl)
library(gridExtra)
library(grid)
library(geosphere)
library(tidyverse)

@@

```{r message=FALSE, warning=FALSE}
# Load the main eLife data file
elife <- read_excel("~/Dropbox/eLife/data/elife_datafile.xlsx")
## What do we have to do to get this to work?

# Two solutions:
# The first is that we do the matching as normal, and then simply lookup the information later
# The second is that we load everything into the tbale at once, and have a different variable name for each

# I will try to get the first to work. 
#
# Load the country infomration .csv file, which was manually created and available along with this file
institution_mapping <- read_csv("https://www.dropbox.com/s/5pcbzhb3v9prwhu/elife_institutions.csv?dl=1")[, 2:3]
country_data <- read_csv("https://www.dropbox.com/s/o2t6724ugp8dzev/country_data_coords.csv?dl=1")

country_mapping <- country_data %>% select(Country, continent, name) %>% rename(Mapping = name, Continent = continent)

@@

  left_join(institution_mapping, by = c("ca_institution" = "elife_institution")) %>%
    ca_institution_rank = THE_rank
  select(-THE_rank) %>%
  left_join(institution_mapping, by = c("fa_institution" = "elife_institution")) %>%
    fa_institution_rank = THE_rank
  select(-THE_rank) %>%
  left_join(institution_mapping, by = c("la_institution" = "elife_institution")) %>%
    la_institution_rank = THE_rank
  select(-THE_rank) %>%
  left_join(institution_mapping, by = c("se_institution" = "elife_institution")) %>%
    se_institution_rank = THE_rank
  select(-THE_rank) %>%
  left_join(institution_mapping, by = c("reviewer1_institution" = "elife_institution")) %>%
    reviewer1_institution_rank = THE_rank
  select(-THE_rank) %>%
  left_join(institution_mapping, by = c("reviewer2_institution" = "elife_institution")) %>%
    reviewer2_institution_rank = THE_rank
  select(-THE_rank) %>%
  left_join(institution_mapping, by = c("reviewer3_institution" = "elife_institution")) %>%
    reviewer3_institution_rank = THE_rank
  select(-THE_rank) %>%
  left_join(institution_mapping, by = c("reviewer4_institution" = "elife_institution")) %>%
    reviewer4_institution_rank = THE_rank
  select(-THE_rank) %>%

@@

    # Flag data if full submission has been submitted, but no decision has been made (ie: still in revision or decision stage)
    full_decision_made = has_full_submission & dplyr::last(na.omit(c(full_decision, rev1_decision, rev2_decision))) != "Revise",

@@

    # Now add variables relating to the composition of the reviewer team
    # Quality of list variables—list of the names, countries, and genders of reviewers
    reviewer_names = list(tolower(na.omit(c(bre_name, reviewer1_name, reviewer2_name, reviewer3_name, reviewer4_name)))),
    reviewer_genders = list(na.omit(c(bre_gender, reviewer1_gender, reviewer2_gender, reviewer3_gender, reviewer4_gender))),
    reviewer_countries = list(tolower(na.omit(c(bre_country, reviewer1_country, reviewer2_country, reviewer3_country, reviewer4_country)))),
    reviewer_continents = list(tolower(na.omit(c(bre_continent, reviewer1_continent, reviewer2_continent, reviewer3_continent, reviewer4_continent)))),
    reviewer_institutions = list(tolower(na.omit(c(bre_institution, reviewer1_institution, reviewer2_institution, reviewer3_institution, reviewer4_institution)))),

@@

    # Geographic distance between the country of the corresponding author and the senior editor
    ca_se_dist = distm(c(subset(country_data, name == ca_country)$Longitude[1], subset(country_data, name == ca_country)$Latitude[1]),
                       c(subset(country_data, name == se_country)$Longitude[1], subset(country_data, name == se_country)$Latitude[1]))[1],

    la_bre_dist = distm(c(subset(country_data, name == la_country)$Longitude[1], subset(country_data, name == la_country)$Latitude[1]),
                       c(subset(country_data, name == bre_country)$Longitude[1], subset(country_data, name == bre_country)$Latitude[1]))[1],

    # Mean geographic distance between country of last author and each of the countries of associated reviewers
    la_reviewer_dist = sum(unlist(sapply(unlist(reviewer_countries), function(rev_country) {
        #print(rev_country)
        if(is.na(rev_country) | is.na(la_country)) return(NA)

        la_coords = c(subset(country_data, name == la_country)$Longitude[1], subset(country_data, name == la_country)$Latitude[1])
        rev_coords = c(subset(country_data, tolower(name) == rev_country)$Longitude[1], subset(country_data, tolower(name) == rev_country)$Latitude[1])
        return(distm(la_coords, rev_coords)[1])
    })), na.rm = T),

    # Mean geographic distance between country of first author and each of the countries of associated reviewers
    fa_reviewer_dist = sum(unlist(sapply(unlist(reviewer_countries), function(rev_country) {
        if(is.na(rev_country) | is.na(fa_country)) return(NA)

        la_coords = c(subset(country_data, name == fa_country)$Longitude[1], subset(country_data, name == fa_country)$Latitude[1])
        rev_coords = c(subset(country_data, tolower(name) == rev_country)$Longitude[1], subset(country_data, tolower(name) == rev_country)$Latitude[1])
        return(distm(la_coords, rev_coords)[1])
    })), na.rm = T),

    # Indicator variables about whether or not any of the above distances are zero
    ca_se_dist_zero = ifelse(is.na(ca_se_dist), NA, ifelse(ca_se_dist == 0, T, F)),
    la_reviewer_dist_zero = ifelse(is.na(la_reviewer_dist), NA, ifelse(la_reviewer_dist == 0, T, F)),
    fa_reviewer_dist_zero = ifelse(is.na(fa_reviewer_dist), NA, ifelse(fa_reviewer_dist == 0, T, F)),

    any_reviewer_from_africa = any(unlist(reviewer_continents) == "africa"),
    any_reviewer_from_north_america = any(unlist(reviewer_continents) == "north america"),
    any_reviewer_from_south_america = any(unlist(reviewer_continents) == "south america"),
    any_reviewer_from_europe = any(unlist(reviewer_continents) == "europe"),
    any_reviewer_from_asia = any(unlist(reviewer_continents) == "asia"),

@@

    la_bre_country_homophily = bre_country == la_country,

@@

    la_bre_continent_homophily = bre_continent == la_continent,

@@

```{r}
full <- elife %>% 
  filter(has_full_submission & final_decision_made) %>%
  filter(la_gender %in% c("M", "F")) %>%
  filter(composition != "Uncertain")

summary(glm(accepted ~ la_gender * composition, data = full, family = "binomial"))
```

@@

elife <- elife %>%
  # Now lets remove any identifying information, ie: names and institutions. We also remove country/continent for gatekeepers, as the population is smaller
  # We also remove all dates and times, because thees could probably be used to identify information about a particular manuscript
  # Also, lets remove variables that we will not prefently be working with, just to keep the table clean
  select(-c(
         ca_name, la_name, fa_name,  se_name, bre_name, reviewer1_name, reviewer2_name, reviewer3_name, reviewer4_name, 
         ca_institution, la_institution, fa_institution, se_institution, bre_institution, 
         reviewer1_institution, reviewer2_institution, reviewer3_institution, reviewer4_institution,
         se_country, bre_country, reviewer1_country, reviewer2_country, reviewer3_country, reviewer4_country,
         initial_submission_time, full_submission_date, rev1_submission_date, rev2_submission_date,
         initial_decision_time, full_decision_date, rev1_decision_date, rev2_decision_date, submission_month,
         deltatime_initial_submission_decision,	deltatime_full_submission_decision,	deltatime_initial_submission_to_accept,	deltatime_full_submission_to_accept,
         deltatime_rev1,	deltatime_rev2,	revision_time,	deltatime_final,
         prop_male_reviewers, prop_female_reviewers, appeal_state1, appeal_state2, appeal_state3, type.x, type.y,
         reviewer_names, reviewer_countries, reviewer_continents, reviewer_genders, full_decisions, reviewer_institutions,
         reviewer_names_nobre, reviewer_genders_nobre))

# write this file as output, so that future analysis can start from this file as a checkpoint
write.csv(elife, "~/Dropbox/eLife/formatted_data/formatted_elife.csv")

write.csv(people, "~/Dropbox/eLife/formatted_data/elife_people.csv")

@@

## Checkpoint
Here we load the data that was manipulated in the previous code chunk. Skip to here if the original (non-anonymized) data is not available.
```{r}
elife <- read.csv("~/Dropbox/eLife/formatted_data/formatted_elife.csv")
```

@@

fig4 <- data_fig4 %>%
  ggplot(aes(x = gender, y = measurement, color = factor(gender), shape = factor(gender), fill = factor(gender))) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, color = "black") +
  geom_text(aes(x = 1.5, y = 0.89, label = ifelse(measure_key == "Submissions", "", as.character(sig))), color = "black") +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  #facet_grid(author_key ~ measure_key) +
  facet_wrap(~author_key) +
  coord_cartesian(ylim = c(0, 1.0)) +
  theme_dakota() +
  guides(fill = F) +
  labs(
    x = "Gender of Author",
    y = "% of full submissions accepted"
  )

@@

data_fig5 <- elife %>%
  filter(initial_decision_made & full_decision_made & !is.na(composition)) %>%
  mutate(total_submissions = n()) %>%
  gather(author_key, value = gender, la_gender) %>%
  filter(gender %in% c("M", "F")) %>%
  group_by(composition, author_key, gender) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE),
    acceptance_rate = sum(accepted == TRUE) / paper_count,
    standard_error = 1.96 * sqrt( (acceptance_rate * (1 - acceptance_rate)) / paper_count),
    lower = acceptance_rate - standard_error,
    upper = acceptance_rate + standard_error
  ) %>%
  ungroup() %>%
  left_join(sig_df, by = c("composition", "author_key")) %>%
  mutate(
    author_key = factor(author_key,
                        levels = c("ca_gender", "fa_gender", "la_gender"),
                        labels = c("ca_gender" = "Corresponding", "fa_gender" = "First", "la_gender" = "Last"))
    ,
    gender = ifelse(gender == "M", "Male", "Female"),
    composition = factor(composition, labels = c("All Men" = "All-male", "All Women" = "All-female", "Mixed" = "Mixed-gender", "Uncertain" = "Uncertain"))
  ) %>%
  filter(composition != "Uncertain")

fig5 <- data_fig5 %>% 
  ggplot(aes(x = gender, y = acceptance_rate, fill = gender)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_text(aes(y = 0.05, label = paper_count), size = 3.5, color = "black") +
  #geom_text(aes(y = 0.1, label = paste0(round(acceptance_rate, 3) * 100, "%")), size = 2.5, color = "black", position = position_dodge(0.87)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, color = "black", alpha = 0.8) +
  geom_text(aes(x = 1.5, y = 0.89, label = sig), color = "black") +
  #geom_text(aes(x = gender, y = 0.1, label = round(acceptance_rate, 3) * 100 ), color = "black") +
  geom_segment(aes(x = 1.1, xend = 1.9, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap( ~composition) +
  coord_cartesian(ylim = c(0.0, 1.0)) +
  theme_dakota() +
  guides(fill = F) +
  labs(y = "% of full submissions accepted",
       x = "Gender of Last Author"
  )

@@

```{r}
g <- grid.arrange(fig4, fig6, ncol = 2, widths = 1:2)

ggsave("~/Desktop/combined_figure.png", g,  width = 12, height = 6)
```

@@

### Proportion of intiial submissions constituted by top 8 counties
```{r}
sum(data_table$`Prop. of initial submissions`)
```

### Proportion of full submissions constituted by top 8 counties
```{r}
sum(data_table$`Prop. of full submissions`)
```

### Proportion of accepted submissions constituted by top 8 counties
```{r}
sum(data_table$`Prop. of accepted submissions`)
```

@@

```{r message=FALSE, warning=FALSE}
countries <- c("Canada", "China", "France", "Germany", "Japan", "Switzerland", "United Kingdom", "United States")
sig_list <- list()

for (country in countries) {
  print(country)
  s <- subset(elife, full_decision_made == T & has_full_submission & ca_country == country)
  t <- table(s$ca_country_homophily, s$accepted)
  test = chisq.test(t[, 1:2])
  sig_list[length(sig_list) + 1] <- list(country = test)
}

@@

```{r message=FALSE, warning=FALSE}
countries <- c("Canada", "China", "France", "Germany", "Japan", "Switzerland", "United Kingdom", "United States")
sig_list <- list()

for (country in countries) {
  print(country)
  s <- subset(elife, full_decision_made == T & has_full_submission & ca_country == country)
  t <- table(s$ca_country_homophily, s$accepted)
  test = chisq.test(t[, 1:2])
  sig_list[length(sig_list) + 1] <- list(country = test)
}

elife %>%
  filter(full_decision_made & has_full_submission & ca_country %in% countries & !is.na(ca_bre_country_homophily)) %>%
  group_by(ca_country, ca_bre_country_homophily) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_accept_rate = accept_count / paper_count,
    se = 1.96 * sqrt( (encourage_accept_rate * (1 - encourage_accept_rate)) / paper_count),
    lower = encourage_accept_rate - se,
    upper = encourage_accept_rate + se,
    upper = ifelse(upper > 1, 1, upper)
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  left_join(sig_df) %>%
  #top_n(16, totals) %>% # 8 countries, 3 authorship types per country, therefore first 24 rows
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>%
  # Start ggplot
  ggplot(aes(x = ca_bre_country_homophily, y = encourage_accept_rate, fill = ca_bre_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 0.075), size = 2.5) +
  geom_text(aes(label = sig, x = 1.5, y = 0.95)) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap(~ca_country, nrow = 2, ncol = 4) +
  ylim(0, 1) +
  theme_dakota() +
  guides(fill = FALSE) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  labs(
    x = "",
    y = "% of full submissions accepted"
  ) +
  theme(
    axis.text.x = element_text(angle = 20, vjust = 1, hjust = 1)
  )

@@

fig7.B <- d1.summ %>%
  union(d2.summ) %>%
  union(d3.summ) %>%
  left_join(sig_df, by = "type") %>%
  mutate(type = factor(type, 
                       levels = c("all", "no us", "no founder"),
                       labels = c("All Countries", "Excluding U.S.", "Excluding U.S., U.K., and Germany")
                       )
         ) %>%
  ggplot(aes(x = ca_country_homophily, y = encourage_accept_rate, fill = ca_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 0.32), size = 2.5) +
  geom_text(aes(label = sig, x = 1.5, y = 0.65)) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.6, 1.1), yend = ifelse(sig != "N/A", 0.6, 1.1)), color = "black") +
  facet_wrap(~type, nrow = 3) +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  theme_dakota() +
  guides(fill = FALSE) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  labs(
    x = "",
    y = "% of full submissions accepted"
  )
```

```{r}
g <- grid.arrange(fig5, fig7.A, ncol = 2, widths = 1:2)

ggsave("~/Desktop/combined_figure2.png", g,  width = 12, height = 6)
```

@@

p2 <- elife %>%
  filter(initial_decision_made & (full_decision_made | full_decision_date_isNA) & !is.na(ca_country)) %>%
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>% # capitalize first letter of country stirngs
  group_by(ca_country) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_count = sum(encouraged == TRUE, na.rm = T),
    encourage_rate = encourage_count / paper_count,
    accept_rate = accept_count / sum(!has_full_submission | full_decision_made, na.rm = T),
    encourage_accept_rate = accept_count / sum(has_full_submission & full_decision_made, na.rm = T)
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  top_n(16, totals) %>%
  mutate(
    ca_country = reorder(ca_country, encourage_rate)
  ) %>%
  gather(measure_key, value = measurement, encourage_rate, accept_rate, encourage_accept_rate) %>%
  mutate(measure_key = factor(measure_key, 
                           levels = c("encourage_rate", "encourage_accept_rate", "accept_rate"),
                           labels = c("encourage_rate" = "% of initial submissions encouraged", 
                                      "encourage_accept_rate" = "% of full submissions accepted",
                                      "accept_rate" = "% of initial submissions accepted"
                                      )
                           ) # end factor
  ) %>%
  group_by(measure_key) %>%
  mutate(
    se = 1.96 * sqrt(measurement * (1 - measurement) / paper_count),
    lower = measurement - se,
    upper = measurement + se
  ) %>%
  ggplot(aes(x = ca_country, y = measurement)) +
  geom_bar(stat = "identity", color = "black", fill = "dodgerblue4", alpha = 0.8) +
  geom_text(aes(y = upper, label = paste0(round(measurement, 3) * 100, "%")), size = 2.5, hjust = -0.4, family = "Times") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  facet_wrap(~measure_key, labeller = labeller(key = labels)) +
  theme_dakota() +
  labs(y = "%") +
  coord_flip() +
  ylim(0, 0.75) +
  theme(
    axis.title.y = element_blank()
  )
